### 2017-09-09 paper/evaluation.tex
RQ7 intro

The rationale for this criteria was to ensure compatibility with

@@

We ran each project on each configuration for 10 times with with ten seeds.
Overall, we needed to reran test suites 600 times, 60 times (10x6
configurations) on each project.
Given the low standard deviations observed in our measurements we
consider ten seeds reasonable for this experiment.

@@

>>>>

The rationale for this criteria is to ensure compatibility with

@@

We ran each project on each configuration for \SubjectsReruns{} times.
Overall, we needed to reran test suites 360 times, 18 times (3x6
configurations) on each project.  Given the low standard deviations
observed in our measurements and the aggregated time cost of 360 test
executions, we consider \SubjectsReruns{} reruns reasonable for this
experiment.

@@

\Jbc{Parei aqui}
